### 2021-06-08 paper/report.tex
Move rapid test plot shares to the appendix. Replace plots as agreed.

The model includes several other features, which are crucial to describe the evolution of
the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness \replaced[id=K]{and disease progress}{}\comment[id=K]{sid only supports
differing infectiousness between variants at the moment} can be introduced. With a
probability of 75\% \citep{Hunter2021}, vaccinated agents become immune and they do not
transmit the virus \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.\footnote{75\%
is lower than what is usually reported for after the second dose. We choose it because in
our model does not include booster shots and does not allow for vaccinated individuals to
become infected and transmit the disease which is the case for Covid-19
\citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.}% the sources only report reduced viral shedding and reduced risk of infection.
% Lauterbach calculated that taking the risk of infection * reduced infectiousness given
% infection based on theses studies suggest that given exposure the risk that fully
% vaccinated individuals pose is <10% of an unvaccinated person.
While vaccines are rolled out, priority depends on age and occupation. Agents may
demand two types of tests as described in Figure~\ref{fig:pcr_antigen_tests}. First,
polymerase chain reaction (PCR) tests directly reveal whether an individual is infected
or not. PCR tests require some time to be processed and there are always aggregate
capacity constraints. Second, rapid antigen tests yield immediate results. Specificity
and sensitivity of these tests is set according to data by \cite{Bruemmer2021,
Smith2021} . The sensitivity of the rapid antigen tests depends on the timing of the
test relative to the start of infectiousness.\comment[id=HM]{subsequent PCR tests,
quarantine, work/school}. Demand for rapid tests will depend on policy, e.g., prices,
testing requirements before work, attending school, or visiting restaurants and shops.

@@

Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and
of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially
recorded cases; the \replaced[id=HM]{color}{blue?} line in
Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index \citep{Hale2020},
which tracks the tightness of non-pharmaceutical interventions. We transform the index
so that lower values represent higher levels of restrictions. A value of zero means all
measures incorporated in the index are turned on. The value 1 represents the situation
of mid-September, where half of all restrictions incorporated in the index are
active.\comment[id=HM]{Need to find version of index with a couple of measures, probably
need the API access...}. In the six weeks between mid September and late October, cases
increased by a factor of XX.\comment[id=K]{In the next iteration all empirical data is
in the figures/results/tables/empirical\_analogues.csv}
% the week of Sep 13 had an incidence of 12.4, the week of Oct 18 had 51.
Restrictions were somewhat tightened in mid-October and again in early November. New
infections remained constant throughout November, before rising again in December.

@@

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/rapid_test_demand_shares}

@@

Quickly rising rates in December prompted the most stringent lockdown to this date.
Schools and daycare centers were closed again, so were customer-facing businesses except
for grocery and drug stores. Shortly afterwards, more factors become relevant. Just
after Christmas, the first people were vaccinated with a focus on older age groups and
medical personnel (Figure~\ref{fig:antigen_tests_vaccinations}. By the end of May, just
over 40\% had received at least one dose of a vaccine. Starting in January, rapid tests
\dots These had to be administered by medical doctors or in pharmacies. At-home tests
approved by authorities were ... in March.\comment[id=HM]{update precise
timeline}\comment[id=K]{From a docstring:Bürgertests started in mid March but demand was
very low initially (\url{https://bit.ly/3ehmGcj}). First tests to self-administer became
available starting March 6. However, supply was very limited in the beginning
(\url{https://bit.ly/3xJCIn8}). The first tests were licensed on Feb 24:
\url{https://www.bundesregierung.de/breg-de/themen/coronavirus/zulassung-schnell-test-1861354}}
From the peak of the second wave just before Christmas until the trough in mid-February,
newly detected cases decreased by almost three quarters. The third wave in the spring of
2021 is associated with a rise in the share of the B.1.1.7 variant among all infections,
depicted in Figure~\ref{fig:share_b117}, reaching more than 80\% in
April\comment[id=HM]{Do we have the table somewhere?}\comment[id=K]{Will be part of the
empirical analogues table}. In early March, some NPIs were being relaxed; e.g.,
hairdressers and home improvement stores were allowed to open again to the public. In
some cases, customers were only allowed to enter with a recent negative rapid test
result.

>>>>

The model includes several other features, which are crucial to describe the evolution of
the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness \replaced[id=K]{}{and disease progress}\comment[id=K]{sid only supports
differing infectiousness between variants at the moment} can be introduced. With a
probability of 75\% \citep{Hunter2021}, vaccinated agents become immune and they do not
transmit the virus \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.\footnote{75\%
is lower than what is usually reported for after the second dose. We choose it because in
our model does not include booster shots and does not allow for vaccinated individuals to
become infected and transmit the disease which is the case for Covid-19
\citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.}% the sources only report reduced viral shedding and reduced risk of infection.
% Lauterbach calculated that taking the risk of infection * reduced infectiousness given
% infection based on theses studies suggest that given exposure the risk that fully
% vaccinated individuals pose is <10% of an unvaccinated person.
While vaccines are rolled out, priority depends on age and occupation. Agents may
demand two types of tests as described in Figure~\ref{fig:pcr_antigen_tests}. First,
polymerase chain reaction (PCR) tests directly reveal whether an individual is infected
or not. PCR tests require some time to be processed and there are always aggregate
capacity constraints. Second, rapid antigen tests yield immediate results. Specificity
and sensitivity of these tests is set according to data by \cite{Bruemmer2021,
Smith2021} . The sensitivity of the rapid antigen tests depends on the timing of the
test relative to the start of infectiousness.\comment[id=HM]{subsequent PCR tests,
quarantine, work/school}. Demand for rapid tests will depend on policy, e.g., prices,
testing requirements before work, attending school, or visiting restaurants and shops.

@@

Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and
of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially
recorded cases; the \replaced[id=HM]{color}{blue?} line in
Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index \citep{Hale2020},
which tracks the tightness of non-pharmaceutical interventions. We transform the index so
that lower values represent higher levels of restrictions. A value of zero means all
measures incorporated in the index are turned on. The value 1 represents the situation of
mid-September, where half of all restrictions incorporated in the index are
active.\comment[id=HM]{Need to find version of index with a couple of measures, probably
need the API access...}. In the six weeks between mid September and late October, cases
increased by a factor of 4.% the week of Sep 13 had an incidence of 12.4, the week of Oct 18 had 51.
Restrictions were somewhat tightened in mid-October and again in early November. New
infections remained constant throughout November, before rising again in December.

@@

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_share_rapid_test_in_last_week_and_vaccinated}

@@

Quickly rising rates in December prompted the most stringent lockdown to this date.
Schools and daycare centers were closed again, so were customer-facing businesses except
for grocery and drug stores. Shortly afterwards, more factors become relevant. Just
after Christmas, the first people were vaccinated with a focus on older age groups and
medical personnel (Figure~\ref{fig:antigen_tests_vaccinations}. By the end of May, just
over 40\% had received at least one dose of a vaccine. Starting in January, rapid tests
\dots These had to be administered by medical doctors or in pharmacies. At-home tests
approved by authorities were ... in March.\comment[id=HM]{update precise
timeline}\comment[id=K]{From a docstring:Bürgertests started in mid March but demand was
very low initially (\url{https://bit.ly/3ehmGcj}). First tests to self-administer became
available starting March 6. However, supply was very limited in the beginning
(\url{https://bit.ly/3xJCIn8}). The first tests were licensed on Feb 24:
\url{https://www.bundesregierung.de/breg-de/themen/coronavirus/zulassung-schnell-test-1861354}}
From the peak of the second wave just before Christmas until the trough in mid-February,
newly detected cases decreased by almost three quarters. The third wave in the spring of
2021 is associated with a rise in the share of the B.1.1.7 variant among all infections,
depicted in Figure~\ref{fig:share_b117}, reaching more than 80\% in
April\comment[id=HM]{Do we have the table somewhere?}\comment[id=K]{is in the empirical
analogues table}. In early March, some NPIs were being relaxed; e.g., hairdressers and
home improvement stores were allowed to open again to the public. In some cases,
customers were only allowed to enter with a recent negative rapid test result.
